Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
edit section 4

\sysname is a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
%As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
%It guarantees that:
%(1) the configurations generated from its templates correctly implement the network's policy for {\em any} concrete topology that matches the abstract topology; and (2) if nodes or edges are added or removed in a way compatible
%with the abstract topology, only configurations of devices adjacent to the change ever need to be updated.
%
%This section introduces \sysname using the examples in \S\ref{sec:motivation}.
%, and the following sections detail template generation and formally define the correctness guarantees.
%
When \sysname compiles a policy, it guarantees that the forwarding behavior of the network will be correct for any concrete instantiation of the abstract network, and for any combination of failures that may occur in the concrete network. Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.

@@

\para{Abstract topology}
Abstract topologies in \sysname capture connectivity invariants of the network that hold both when network is first instantiated and as it evolves. These invariantes are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
%
We designed these abstractions to be able to precisely capture most real network topologies, while being amenable to the fault tolerance analysis and configuration synthesis that is done by our compiler.

@@

We introduce our topology abstractions using the networks from \S\ref{sec:motivation}. Topology abstractions consist of several components.
The first is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network. Figure~\ref{fig:example3} shows an example of an abstraction for both datacenter networks from \S\ref{sec:motivation}. In particular the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).

@@

All the guarantees provided by \sysname hold for any instantiation of the abstract network. This means that operators can safely expand their network in the future so long as the new network also satisfies these logical constraints.

>>>>

In this section we give an overview of \sysname, a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
%As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
%It guarantees that:
%(1) the configurations generated from its templates correctly implement the network's policy for {\em any} concrete topology that matches the abstract topology; and (2) if nodes or edges are added or removed in a way compatible
%with the abstract topology, only configurations of devices adjacent to the change ever need to be updated.
%
%This section introduces \sysname using the examples in \S\ref{sec:motivation}.
%, and the following sections detail template generation and formally define the correctness guarantees.
%
When \sysname generates templates, it guarantees that the forwarding behavior of the network will be correct for any instantiation of the templates on a concrete network that repects the abstraction. 
%Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.

@@

\para{Abstract topology}
Abstract topologies in \sysname define structural and role-based invariants that capture a collection of concrete networks. These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities and connectivity.
%
We designed these abstractions to be able to precisely capture most real network topologies, while being amenable to the fault tolerance analysis and configuration synthesis that is done by our compiler.

@@

We introduce our topology abstractions using the networks from \S\ref{sec:motivation}. Topology abstractions consist of several components.
The first is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network. Figure~\ref{fig:example3} shows an example of an abstraction for both datacenter networks from \S\ref{sec:motivation}. In the example, the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).

@@

%All the guarantees provided by \sysname hold for any instantiation of the abstract network. This means that operators can safely expand their network in the future so long as the new network also satisfies these logical constraints.
